---
title: "Statical Inference"
author: "koji"
date: "2022/1/9"
output:
  html_document: 
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exponential Distribution 
Generate 40 random variables and take the mean using rexp()as well (lamda = 0.2, n = 40)
Then, store the mean in "rxp" and repete it 1,000 times
Finally make hitogram of the mns


```{r, echo=FALSE}
rxp <- NULL; lamda <- 0.2
for (i in 1:1000) rxp <- c(rxp, mean(rexp(40, lamda)))
hist(rxp)
```

# 1.Show the sample mean and compare it to the theoretical mean of the distribution.

```{r, echo=FALSE}
print(c("sample mean", mean(rxp))); print(c("theoretical mean", 1/lamda)) 

```
check 95% confidence interval with t.test() and make sure there is no statistical significant between the two means

```{r, echo=FALSE}
t.test(rxp)
```


# 2.Show how variable the sample is(via variance) and compare it to the theoretical variance of the distrubution.
the variance of the distribution is μ^2/n, thus the sample variance and theoretical variance are
```{r, echo=FALSE}
print(c("sample variance", var(rxp)))
print(c("theoretical variance", ((1/lamda)^2)/40))
```

# 3.Show that the distribution is approximately normal

```{r, echo=FALSE}

```

